Introducing Statistical Design of Experiments to SPARQL Endpoint Evaluation

### 2013-07-23 exp1/iswc2013.tex
Remove table 3 and describe it in the text
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@619 43ef1190-90fd-4dd7-a769-d0121f02b80e

We have argued that fixing certain parameters is untenable, but we
have allowed ourselves to disregard caching and warm-up runs. We are
aware that caching may be important in 4store, as a preliminary
experiment gave the results in Table~\ref{tab:cacheexp}. We see that the
response time was significantly lower when an OPTIONAL clause was
added to the query. As this is not more restrictive query, the most
likely explanation is that the result of the evaluation of the Basic
Graph Pattern was cached, so only the OPTIONAL left join was necessary
to add in the second query.

\begin{table}[ht]
\begin{center}
\caption{Two experiments with and without OPTIONAL clause.}\label{tab:cacheexp}
\begin{tabular}{ccccccccr}
  \hline
``Implement'' & ``TripleC'' & ``Machine'' & ``BGPComp'' & ``Lang'' & ``Range'' & ``Union'' & ``Optional'' & Time \\
 \hline
1   &    1  &     1  &     2 &   1 &    1   &  1  & 1 &  53.918049 \\
1   &    1  &     1  &     2 &   1 &    1   &  1  & 2 &   1.252312 \\
   \hline
\end{tabular}
\end{center}
\end{table}

>>>>

We have argued that fixing certain parameters is untenable, but we
have allowed ourselves to disregard caching and warm-up runs. We are
aware that caching may be important in 4store, as a preliminary
experiment gave a response time of 53.9~s of a query with ``BGPComp''
at level~2 but other factors at level~1. When an OPTIONAL clause was
added, the response time dropped to 1.25~s. As this is not more
restrictive query, the most likely explanation is that the result of
the evaluation of the Basic Graph Pattern was cached, so only the
OPTIONAL left join was necessary to add in the second query.
